An in-depth study of Explainability and Adversarial Robustness for RNNs

### 2019-12-16 ex3/paper/paper.tex
Update ars_original figure

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and average modification per flow required by an adversary to make a flow appear benign for CIC-IDS-2017.}
\todo{Show for which attack class not enough adversarial samples could be found.}
\label{fig:recall_ars}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=\columnwidth]{../plots/ars_original.pdf}
\caption{Recall for each attack type and average modification per flow required by an adversary to make a flow appear benign for CIC-IDS-2017. For ``PortScan, Firewall
'' recall never falls under 66\%, meaning that an adversary does not succeed and that \gls{ars} is $\inf$.}
\label{fig:recall_ars}
\end{figure}
